### 2015-07-08 text/ms.Rmd
Tweak intro

\noindent Ecological population status and trajectory are two of the most
fundamental values to quantify in ecological resource management [e.g.
@mace2008]. Population status and trajectory are key to everything from global
assessments of extinction risk [e.g. @stuart2004; @schipper2008;
@juan-jorda2011] to local management of hunting (REF) and fishing (REF). But
ecological resource managers are often faced with reconciling multiple
uncertain and potentially conflicting estimates of these quantities---some
models may suggest a population is at risk and declining in abundance while
others may suggest it is not at risk and stable (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@araujo2007]. For instance,
REF-international did this and REF-national did this...

Whereas averages or weighted averages can improve predictions, they may not
optimally leverage available data. The truth does not necessarily lie in the
middle of multiple model predictions. Some models perform better than others in
certain conditions and the covariance between model predictions may contain
information that can improve predictions. We can exploit these characteristics
by using the predictions from a group of models as inputs into a separate
statistical model. This technique, sometimes called 'superensemble' modelling,
is common in climate and weather forecasting [@krishnamurti1999]. The
superensemble is fit to some training dataset where outcomes are well known and
used to predict on a dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble considerably
outperformed any individual prediction or weighted average of predictions in
terms of accuracy.

>>>>

\noindent Ecological population status and trajectory are two of the most
fundamental values to quantify in ecological resource management [e.g.
@mace2008]. Population status and trajectory are key to everything from global
assessments of extinction risk [e.g. @stuart2004; @schipper2008;
@juan-jorda2011] to local management of hunting (REF) and fishing (REF). But
ecological resource managers are often faced with reconciling multiple
uncertain and potentially conflicting estimates of these quantities. For
example, some models may suggest a population is at risk and declining in
abundance while others may suggest it is not at risk and stable (e.g. REF).

One solution is to take the average or weighted average of an ensemble of model
predictions. Such ensembles are typically more accurate and less biased than
individual model estimates and can integrate uncertainty in model structure,
initial conditions, and parameter estimation [@araujo2007]. For instance,
REF-IUCN did this and REF-COSEWIC did this...

Whereas averages or weighted averages can improve predictions, they may not
optimally leverage available data. The truth does not necessarily lie in the
middle of multiple model predictions, some models perform better than others in
certain conditions, and the covariance between model predictions may contain
information that can improve predictions. We can exploit these characteristics
by using the predictions from a group of models as inputs into a separate
statistical model. This technique, sometimes called 'superensemble' modelling,
is common in climate and weather forecasting [@krishnamurti1999]. The
superensemble is fit to some training dataset where outcomes are well known and
used to predict on a dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.
